---
title: "Tidymodels Workflow"
output:
  html_document: default
  pdf_document: default
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Load the necessary libaries
```{r echo=TRUE, message=FALSE, warning=FALSE}

library(tidyverse)
library(tidymodels)

```
```{r}
data("ames")
```



# Split data into training and test data set
```{r}
split_ames <- initial_split(ames, strata = Sale_Price, prop = 0.8)

ames_train <- training(split_ames)
ames_test <- testing(split_ames)

```

# Create Cross-Validation data set
```{r}

ames_vfold <- vfold_cv(ames_train) # USe the training data set from the initial split


```
# Create the Model MAtrix and all require pre-processing steps with recipes
```{r}
# Use the full training set for as the data object in the recipe function
# The recipe function shows what pre-processing steps wiill done and the role of the variables
rec_ames <- ames_train %>% recipe(Sale_Price ~ .) %>% 
  step_corr(all_numeric(), -all_outcomes()) # all_numeric and other all_ function need ()

rec_prep <- prep(rec_ames) # prep/bake is only needed when you don't work tune_grid
 
  
#the Prep function applies the preprocessing steps to the data object
rec_ames
rec_prep
```

Creare model
```{r}

lm_ames <- linear_reg() %>% set_engine("lm")

```

# Create a workflow object 
```{r}
# add the basic recipe without calling the prep() function on it - The basic reciped needs a # data object for establishing the parameters for thre pre-processing -e.g. include complete # training dataset 
# add the model definition - No data obejct is included
ames_work <- workflow() %>% add_recipe(rec_ames) %>%
 add_model(lm_ames)
```



###Fitting or Tuning

fit_resamples(object, ...)

# S3 method for model_spec
fit_resamples(
  object,
  preprocessor,
  resamples,
  ...,
  metrics = NULL,
  control = control_resamples()
)

# S3 method for workflow
fit_resamples(
  object,
  resamples,
  ...,
  metrics = NULL,
  control = control_resamples()
)
ARGUMENTS
object	
A parsnip model specification or a workflows::workflow(). No tuning parameters are allowed.

...	
Currently unused.

preprocessor	
A traditional model formula or a recipe created using recipes::recipe().

resamples	
A resample rset created from an rsample function such as rsample::vfold_cv().

metrics	
A yardstick::metric_set(), or NULL to compute a standard set of metrics.

control	
A control_resamples() object used to fine tune the resampling process.

PERFORMANCE METRICS


